---
title: "Figure 1 & Table 1 - Holocene Hydroclimate Proxy Summary"
author: "Chris Hancock"
output: html_document
---

#### Load Packages

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(cowplot)
library(egg)
library(geoChronR)
library(ggrepel)
library(ggplot2)
library(ggstar)
library(lipdR)
library(maptools)
library(proj4)
library(RColorBrewer)
library(rworldmap)
library(scales)
library(sp)
library(tidyverse)

print("Packages Loaded")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Set Working Directory

wd = '/Volumes/GoogleDrive/My Drive/zResearch/Manuscript/2021_HoloceneHydroclimate/2021_HoloceneHydroclimate/'
#knitr::opts_knit$set(root.dir = wd)
```

#### Load Data

```{r echo=TRUE, message=FALSE, warning=FALSE}
var     <- 'HC'
lipdTSO <- readRDS(file.path(wd,'Data','Proxy','LiPD','lipdData.rds'))[[var]]
proxyDf <- read.csv(file=file.path(wd,'Data','Proxy',paste0('proxyMetaData_',var,'.csv')))
print("Proxy data loaded ")

#Load IPCC region data
load(url('https://github.com/SantanderMetGroup/ATLAS/blob/main/reference-regions/IPCC-WGI-reference-regions-v4_R.rda?raw=true'), verbose = TRUE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Set Projections
PROJ     <- '+proj=robin   +ellps=WGS84 +datum=WGS84 +no_defs +lon_0=0 +x_0=0 +y_0=0 +units=m'
PROJorig <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
#Transform projection
refregions <-  spTransform(IPCC_WGI_reference_regions_v4, CRSobj = PROJ)
#Countries for basemap
countries  <- rworldmap::getMap("less islands")
countries  <- sp::spTransform(countries,  CRSobj = PROJ)
#Transform proxy projections
pointData  <- data.frame(longitude=c(proxyDf$longitude),latitude=c(proxyDf$latitude))
pointData  <- SpatialPointsDataFrame(coords=pointData, data=pointData, 
                                     proj4string=CRS(PROJorig))
pointData  <- spTransform(pointData,CRSobj = PROJ)
proxyDf$lonsPrj <- pointData@coords[,1]
proxyDf$latsPrj <- pointData@coords[,2]
```

#### Figure Settings

```{r echo=TRUE, message=FALSE, warning=FALSE}
save     <- TRUE
specific <- TRUE 

if (save){ print(paste0("save ",var," figs"))
} else{    print(paste0("plot ",var," figs"))}

figFont <- 'Times New Roman'
figText <- 10
figSize <- c(6.5,3)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Colors and Shapes

plotSettings <- vector(mode='list')
Csettings <- c("#92C5DE","#4393C3",'#2166AC')
if (var == 'HC'){
  if(specific){
    plotSettings$names <- sort(unique(proxyDf$CategorySpec))
    #https://carto.com/carto-colors/
    plotSettings$color <- as.character(plotSettings$names)
    plotSettings$color[which(plotSettings$names=="Glacier Ice (Accumulation)")] <- "#5F4690" #"powder blue"
    plotSettings$color[which(plotSettings$names=="Shoreline (Lake Level)")]  <- "#38A6A5" #"corn flower blue"
    plotSettings$color[which(plotSettings$names=="Lake Sediment (δ18O)")]    <- "#1D6996" #"dark blue"
    plotSettings$color[which(plotSettings$names=="Leaf Wax (δD)")]           <- "#94346E" # "dark orchid" #δ
    plotSettings$color[which(plotSettings$names=="Other (calibrated)")]      <- "grey40" #"grey40"
    plotSettings$color[which(plotSettings$names=="Other (not calibrated)")]  <- "grey" #"grey"
    plotSettings$color[which(plotSettings$names=="Pollen (calibrated)")]     <- "#0F8554" #"forest green"
    plotSettings$color[which(plotSettings$names=="Pollen (not calibrated)")] <- "#73AF48" #"" #"yellowgreen"
    plotSettings$color[which(plotSettings$names=="Speleothem (other)")]      <- "#EDAD08" #"darkorange"
    plotSettings$color[which(plotSettings$names=="Speleothem (δ13C)")]       <- "#E17C05" #"lightcoral"
    plotSettings$color[which(plotSettings$names=="Speleothem (δ18O)")]       <- "#CC503E" #"firebrick"
    #
    plotSettings$shape <- as.character(plotSettings$names) 
    plotSettings$shape[which(plotSettings$names=="Glacier Ice (Accumulation)")] <- 12
    plotSettings$shape[which(plotSettings$names=="Shoreline (Lake Level)")]  <- 21
    plotSettings$shape[which(plotSettings$names=="Lake Sediment (δ18O)")]    <- 15
    plotSettings$shape[which(plotSettings$names=="Leaf Wax (δD)")]           <- 5
    plotSettings$shape[which(plotSettings$names=="Other (calibrated)")]      <- 6
    plotSettings$shape[which(plotSettings$names=="Other (not calibrated)")]  <- 13
    plotSettings$shape[which(plotSettings$names=="Pollen (calibrated)")]     <- 14
    plotSettings$shape[which(plotSettings$names=="Pollen (not calibrated)")] <- 1
    plotSettings$shape[which(plotSettings$names=="Speleothem (other)")]      <- 17
    plotSettings$shape[which(plotSettings$names=="Speleothem (δ13C)")]       <- 23
    plotSettings$shape[which(plotSettings$names=="Speleothem (δ18O)")]       <- 11  
  } else{
    plotSettings$names <- sort(unique(proxyDf$Category))
    #
    plotSettings$color <- as.character(plotSettings$names)
    plotSettings$color[which(plotSettings$names=="Glacier Ice")]             <- "powder blue"
    plotSettings$color[which(plotSettings$names=="Shoreline")]               <- "corn flower blue"
    plotSettings$color[which(plotSettings$names=="Lake Sediment (δ18O)")]    <- "dark blue"
    plotSettings$color[which(plotSettings$names=="Leaf Wax (δD)")]           <- "dark orchid"
    plotSettings$color[which(plotSettings$names=="Other")]                   <- "grey"
    plotSettings$color[which(plotSettings$names=="Pollen")]                  <- "forest green"
    plotSettings$color[which(plotSettings$names=="Speleothem")]              <- "firebrick"
    #
    plotSettings$shape <- as.character(plotSettings$names) 
    plotSettings$shape[which(plotSettings$names=="Glacier Ice")]             <- 12
    plotSettings$shape[which(plotSettings$names=="Shoreline")]               <- 21
    plotSettings$shape[which(plotSettings$names=="Lake Sediment (δ18O)")]    <- 15
    plotSettings$shape[which(plotSettings$names=="Leaf Wax (δD)")]           <- 5
    plotSettings$shape[which(plotSettings$names=="Other")]                   <- 13
    plotSettings$shape[which(plotSettings$names=="Pollen")]                  <- 14
    plotSettings$shape[which(plotSettings$names=="Speleothem")]              <- 11
  }
} else if (var == 'T'){
  plotSettings$names <- sort(unique(proxyDf$Category))
  #
  plotSettings$color <- as.character(plotSettings$names)
  plotSettings$color[which(plotSettings$names=="alkenone")]          <- "tomato"
  plotSettings$color[which(plotSettings$names=="biophysical")]       <- "skyblue4"
  plotSettings$color[which(plotSettings$names=="chironomid")]        <- "firebrick"
  plotSettings$color[which(plotSettings$names=="isotope")]           <- "orange"
  plotSettings$color[which(plotSettings$names=="Mg/Ca")]             <- "midnight blue"
  plotSettings$color[which(plotSettings$names=="other biomarker")]   <- "medium blue"
  plotSettings$color[which(plotSettings$names=="other ice")]         <- "powder blue"
  plotSettings$color[which(plotSettings$names=="other microfossil")] <- "plum4"
  plotSettings$color[which(plotSettings$names=="pollen")]            <- "forest green"
  #
  plotSettings$color[which(plotSettings$names=="alkenone")]          <- 22 
  plotSettings$color[which(plotSettings$names=="biophysical")]       <- 1 
  plotSettings$color[which(plotSettings$names=="chironomid")]        <- 30 
  plotSettings$color[which(plotSettings$names=="isotope")]           <- 15 
  plotSettings$color[which(plotSettings$names=="Mg/Ca")]             <- 25 
  plotSettings$color[which(plotSettings$names=="other biomarker")]   <- 13 
  plotSettings$color[which(plotSettings$names=="other ice")]         <- 12
  plotSettings$color[which(plotSettings$names=="other microfossil")] <- 5 
  plotSettings$color[which(plotSettings$names=="pollen")]            <- 14 
}
plotSettings$shape <- as.numeric(plotSettings$shape)

```

#### Summary Table (Table 1)

```{r echo=TRUE, message=FALSE, warning=FALSE}
#Summarize metadata by category
pivot <- proxyDf %>%
  group_by(CategorySpec) %>%
  dplyr::summarize(count =  n(),
            ageRange     = median(ageRange),
            ageRes       = median(ageRes),
            ageCtrlN     = median(ageCtrlN,na.rm=TRUE),
            ageCtrlMax   = median(ageCtrlMax,na.rm=TRUE),
            pctChronData = NA)

#Manually change rows to desired order
pivot <- pivot[c(1,2,3,6,7,8,11,10,9,4,5),]

#Add "All" row
pivot[12,] <- proxyDf %>%
  dplyr::summarize(CategorySpec='All', count =  n(),
            ageRange     = median(ageRange),
            ageRes       = median(ageRes),
            ageCtrlN     = median(ageCtrlN,na.rm=TRUE),
            ageCtrlMax   = median(ageCtrlMax,na.rm=TRUE),
            pctChronData = NA)

#Calc % of records with age control
summary <- proxyDf[which(!is.na(proxyDf$ageCtrlMax)),]
summary <- summary[which(summary$archive %in% c('Wood','GlacierIce') == FALSE),]
summary <- summary[which(summary$Category != 'Shoreline'),]
diff    <- as.character(round(100*(length(which(proxyDf$archive %in% c('Wood','GlacierIce')) 
                                  + which(proxyDf$Category == 'Shoreline')))/nrow(proxyDf)))
pivot[12,'pctChronData'] <- as.character(round(100*nrow(summary)/nrow(proxyDf)))
pivot[12,'pctChronData'] <- paste0(pivot[12,'pctChronData'],'+',diff)
summary <- summary %>% group_by(CategorySpec) %>% dplyr::summarize(count =  n())

for (cat in summary$CategorySpec){
  n   = summary[which(summary$CategorySpec==cat),2]
  pct = 100*n/pivot[which(pivot$CategorySpec==cat),'count']
  pivot[which(pivot$CategorySpec==cat),'pctChronData'] <- as.character(round(pct))
}

pivot
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### BaseMap
#Create Plot
basePlot <- ggplot(proxyDf)+
  scale_y_continuous(name="Count of Records", oob=scales::squish, limits=c(0,150), expand=c(0,0))+
  theme_bw()+
  theme(text = element_text(family=figFont,size=figText),
        plot.background = element_rect(fill = 'White',color='Black'),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "in"),
        legend.key.height = unit(0.12, "in"),
        legend.key.width = unit(0.1, "in"),
        legend.title = element_blank(),
        legend.position = 'none')
#BaseMap
IPCC <- TRUE
basemap <- ggplot() +
  borders(aggregate(refregions, FUN=length), fill=NA, color='black', size=2) +
  geom_map(data=refregions, map=fortify(refregions), 
           aes(x=long, y=lat, group=group, map_id=id), fill="white", color="white", size=1)+
  geom_map(data=countries,  map=fortify(countries),  
           aes(x=long, y=lat, group=group, map_id=id), fill ="grey80",color="grey90",size=0.2) +
  coord_fixed(1) + 
  theme_void() 
if (IPCC){ 
  basemap <- basemap +
    geom_map(data=subset(refregions, Acronym %in% proxyDf$ipccReg), 
             map=fortify(subset(refregions, Acronym %in% proxyDf$ipccReg)), 
             aes(x=long, y=lat, group=group, map_id=id),
             alpha=0.75, size=0.3, color='black' , fill=NA,linetype = "dashed") 
}

```

#### Plot sample resolution histogram (only Holocene ages)

```{r}

#Summarize dataframe by source
pieData    <- proxyDf %>% 
  group_by(source) %>% 
  dplyr::summarize(count =  n())

#Change names to be more descriptive
names <- as.character(pieData$source)
i <-  which(names=='Arctic Holocene')
names[i] <- paste0('Arctic Holocene (Sundqvist et al., 2014)',
                   ' (n=',as.character(pieData$count[i]),')')
i <-  which(names=='Iso2k')
names[i] <- paste0('Iso2k (Konecky et al., 2020)',
                   ' (n=',as.character(pieData$count[i]),')')
i <-  which(names=='Other')
names[i] <- paste0('Miscellaneous',
                   ' (n=',as.character(pieData$count[i]),')')
i <-  which(names=='SISALv2')
names[i] <- paste0('SISALv2 (Comas-Bru et al., 2020)',
                   ' (n=',as.character(pieData$count[i]),')')
i <-  which(names=='Oxford Lake Level Database')
names[i] <- paste0('Oxford Lake Level Database (Street-Perrott et al., 1989)',
                   ' (n=',as.character(pieData$count[i]),')')
i <-  which(names=='Liefert and Shuman, 2020 ')
names[i] <- paste0('N.A. Lake Level Database (Liefert and Shuman, 2020)',
                   ' (n=',as.character(pieData$count[i]),')')
i <-  which(names=='Legacy Climate v1.0')
names[i] <- paste0('Legacy Climate v1.0 (Herzschuh et al., 2022)',
                   ' (n=',as.character(pieData$count[i]),')')
i <-  which(names=='Mid-Latitude Holocene')
names[i] <- paste0('Mid-Latitude Holocene (Routson et al., 2019)',
                   ' (n=',as.character(pieData$count[i]),')')
i <-  which(names=='wNA')
names[i] <- paste0('Western North America (Routson et al., 2021)',
                   ' (n=',as.character(pieData$count[i]),')')
pieData$source <- names

#Arrange in alphabetical order 
pieData <- pieData %>% arrange(source)
#Cumulative sum to id where to plot on graph
pieData$pos <- cumsum(pieData$count)

#Plot pie chart for source
pie <- ggplot(pieData,aes(x="", y=count, fill=source)) +
  geom_bar(stat="identity", width=1, color= 'black') +
  coord_polar("y", start=0) +
  scale_fill_manual(values=c("powder blue","dark blue","forest green","royal blue","yellowgreen",
                             "grey","corn flower blue","firebrick","orange"),name='Data Source') +
  theme_void() + 
  theme(text = element_text(family=figFont,size=figText),
        plot.background = element_rect(fill = 'white',color='Black'),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "in"),
        legend.key.height = unit(0.15, "in"),
        legend.key.width = unit(0.15, "in"))
        #legend.title = element_blank())#,legend.position = 'none')# legend.position = c(0.5,0.7))
if (save) {
  ggsave(plot=pie , width = figSize[1], height = figSize[2], units='in', dpi = 600,
       filename = file.path(wd,"Figures","Proxy","PlotProxySource.png"))
}
print("Summary of data source for proxy data")
pie
```

#### Plot sample resolution histogram (only Holocene ages)

```{r echo=TRUE, message=FALSE, warning=FALSE}
plotData <- proxyDf[,'ageRes']
binsize <- 30

plotRes <- basePlot+
  geom_vline( xintercept=median(plotData), size=0.8) +
  #geom_vline(xintercept=mean(  plotData), size=0.8, linetype=2) +
  geom_histogram(aes(plotData, fill=CategorySpec), color='Black', alpha=0.7, 
                 breaks = c(0,binsize/2,seq(binsize,max(plotData,na.rm=TRUE)+binsize,binsize))) +
  scale_fill_manual(values=plotSettings$color) +
  scale_x_continuous(name=paste0("Median Proxy Sample Resolution (binwidth = ",binsize," years)") ,
                     limits=c(0,max(plotData,na.rm=TRUE)+binsize/2), expand=c(0,0),
                  breaks=seq(0,max( plotData,na.rm=TRUE),300)) +
  scale_y_continuous(name="Count of Records", oob=scales::squish, limits=c(0,150), expand=c(0,0))+
  theme(legend.position = c(0.8,0.5))

if (save) {
  ggsave(plot=plotRes, width = figSize[1], height = figSize[2], units='in', dpi = 600,
         filename = file.path(wd,"Figures","Proxy","PlotProxyAgeRes.png"))
}
print(paste("Mean:",as.character(round(mean(plotData)))))
print(paste("Median:",as.character(round(median(plotData)))))
print(paste("Range:",as.character(round(range(plotData)))))

plotRes
```

#### Plot record length histogram (only Holocene ages)

```{r echo=TRUE, message=FALSE, warning=FALSE}
plotData <- proxyDf[,'ageRange']
binsize <- 500

plotRange <- basePlot+
  geom_vline( xintercept=median(plotData), size=0.8) +
  #geom_vline(xintercept=mean(  plotData), size=0.8, linetype=2) +
  geom_histogram(aes(plotData, fill=CategorySpec), color='Black', alpha=0.7, 
                 breaks = c(0,seq(binsize,max(proxyDf[,'ageRange'],na.rm=TRUE)+binsize,binsize))) +
  scale_fill_manual(values=plotSettings$color) +
  scale_x_continuous(name = paste("Record Length (binwidth =",binsize,"years)"),
                     limits=c(4000,12000),expand=c(0,0),breaks=seq(3000,12000,2000)) +
  scale_y_continuous(name="Count of Records", oob=scales::squish, limits=c(0,350), expand=c(0,0))+
  theme(legend.position = c(0.2,0.5))
  
if (save) {
  ggsave(plot=plotRange, width = figSize[1], height = figSize[2], units='in', dpi = 600,
         filename = file.path(wd,"Figures","Proxy","PlotProxyAgeRange.png"))
}
print(paste("Mean:",as.character(round(mean(plotData)))))
print(paste("Median:",as.character(round(median(plotData)))))
print(paste("Range:",as.character(round(range(plotData)))))

plotRange
```

#### Plot age control histogram (only Holocene ages)

```{r echo=TRUE, message=FALSE, warning=FALSE}
plotData <- proxyDf[,'ageCtrlMax']
binsize <- 500

plotChron <- basePlot+
  geom_vline( xintercept=median(plotData), size=0.8) +
  #geom_vline(xintercept=mean(  plotData), size=0.8, linetype=2) +
  geom_histogram(aes(plotData, fill=CategorySpec), color='Black', alpha=0.7, 
                 breaks = c(0,seq(binsize,max(proxyDf[,'ageRange'],na.rm=TRUE)+binsize,binsize))) +
  scale_fill_manual(values=plotSettings$color[-c(1)]) +
  scale_x_continuous(name = paste("Maximum Age Control Gap (binwidth =",binsize,"years)"),
                     limits=c(0,6000),expand=c(0,0),breaks=seq(0,6000,1000)) +
  #scale_y_continuous(name="Count of Records", oob=scales::squish, limits=c(0,150), expand=c(0,0))+
  theme(legend.position = c(0.8,0.5))
  
if (save) {
  ggsave(plot=plotChron, width = figSize[1], height = figSize[2], units='in', dpi = 600,
         filename = file.path(wd,"Figures","Proxy","PlotProxyAgeControl.png"))
}
print(paste("Mean:",as.character(round(mean(plotData)))))
print(paste("Median:",as.character(round(median(plotData)))))
print(paste("Range:",as.character(round(range(plotData)))))

plotChron
```

#### Plot time density

```{r  echo=TRUE, message=FALSE, warning=FALSE}
plotTimeData <- plotTimeAvailabilityTs(lipdTSO,age.range = c(0,12000),step=100,group='CategorySpecific')
plotTime <- ggplot(plotTimeData$data,aes(yvec,value))+
  geom_area(alpha=0.9,aes(fill=group),color='Black',size=0.2)+
  scale_fill_manual(values=plotSettings$color) +
  scale_x_reverse(name = "Age (yr BP)", limits=c(12000,0),expand=c(0,0),n.breaks=7)+
  scale_y_continuous(name = "Count of Records",limits=c(0,length(lipdTSO)),expand=c(0,0),
                     labels=seq(0,length(lipdTSO),100), breaks=seq(0,length(lipdTSO),100))+
  theme_bw()+
  theme(text = element_text(family=figFont,size=figText),
        plot.background = element_rect(fill = 'White',color='Black'),
        plot.margin = unit(c(0, 0.1, 0.1, 0.1), "in"),
        legend.key.height = unit(0.1, "in"),
        legend.key.width = unit(0.1, "in"),
        legend.title = element_blank())#,legend.position = 'none')# legend.position = c(0.5,0.7))

if (save) {
  ggsave(plot=plotTime, width = figSize[1], height = figSize[2], units='in', dpi = 600,
         filename = file.path(wd,"Figures","Proxy","PlotTimeAvailability.png"))
}
plotTime
```

#### Map proxy data

```{r  message=TRUE, warning=FALSE}
proxyMapSites <- basemap+
  #Proxy Data
  geom_star(data= as.data.frame(proxyDf),aes(x=lonsPrj , y=latsPrj,
                                                  starshape=CategorySpec, fill=CategorySpec),
            size=1.75,color='Black',alpha=1,starstroke=0.3) + 
  scale_fill_manual(values=plotSettings$color,name= 'Proxy Category') +
  scale_starshape_manual(values=plotSettings$shape,name= 'Proxy Category') +
  #Theme
  theme(text = element_text(family=figFont,size=figText),
        plot.background = element_rect(fill = 'white',color='white'),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.4), "in"),
        legend.background =  element_rect(fill = alpha('white', 0.85),size=0.5),#alpha=0.5),
        legend.margin = margin(c(0, 0.1, 0.05, 0.06), unit="in"),
        legend.key.height = unit(0.12, "in"),
        legend.key.width = unit(0.12, "in"),
        legend.position = c(0.12,0.32),
        legend.title = element_blank())#,legend.position = 'none')# legend.position = c(0.5,0.7))
if (save) {
  ggsave(plot=proxyMapSites, width = 6.5, height = 3.25, dpi = 600, 
       filename = file.path(wd,"Figures","Proxy",paste('PlotProxyTypeRegion_',var,'.png',sep='')))
}
proxyMapSites
```

#### Combine proxy map with time density plot

```{r message=FALSE, warning=FALSE}
fig1 <- ggarrange(proxyMapSites+ theme(legend.position = c(0.1,0.3)), 
                  plotTime+      theme(legend.position = 'none',
                                       plot.margin = unit(c(0, 0.5, 0.1, 0.4), "in")),
                 ncol=1, widths=c(6.5), heights=c(3.25,1.75), padding=0)
if (save) {
  ggsave(plot=fig1, width = 6.5, height = 5, dpi = 600,
       filename = file.path(wd,"Figures","Proxy",paste('Figure1_',var,'_ProxyMapwithTime.png',sep='')))
}
```

#### Plot number of records in each region.

```{r  message=FALSE, warning=FALSE}
dataTable <- fortify(subset(refregions, Acronym %in% proxyDf$ipccReg))
dataTable$Count     <- NA
dataTable$CountName <- NA
dataTable$Region    <- NA

#Set Breaks and color scheme with lowest group as grey
figBreaks <- c(5,10,15,20,30,50,80)
figlabels <- c(paste("<",figBreaks[1]+1),
               paste(as.character(figBreaks[-length(figBreaks)]+1),"-",as.character(figBreaks[-1])),
               paste(">",figBreaks[length(figBreaks)]))
figPalette <- c("#CCCCCC",RColorBrewer::brewer.pal(n=7, name = "YlOrRd"))

#Count number of records in each region
for (reg in unique(dataTable$id)){
  i     <- which(refregions@data[["Acronym"]]==reg)
  count <- length(which(proxyDf$ipccReg      ==reg))
  if (count == 0){                   countName <- NA
  } else if (count <= figBreaks[1]){ countName <- 0
  } else if (count <= figBreaks[2]){ countName <- 1
  } else if (count <= figBreaks[3]){ countName <- 2
  } else if (count <= figBreaks[4]){ countName <- 3
  } else if (count <= figBreaks[5]){ countName <- 4
  } else if (count <= figBreaks[6]){ countName <- 5
  } else if (count <= figBreaks[7]){ countName <- 6
  } else {countName <- 7}
  dataTable$Count[    which(dataTable$id==reg)] <- count
  dataTable$CountName[which(dataTable$id==reg)] <- countName
  dataTable$Region[   which(dataTable$id==reg)] <- reg
}

#Plot
proxyMapRegions <- basemap + 
  #Add refrence regions boundaries
  geom_map(data=subset(refregions, Acronym %in% proxyDf$ipccReg), 
           map=dataTable, alpha=0.75, size=0.5, color='black' , 
           aes(x=long, y=lat, group=group, map_id=id,fill=as.factor(dataTable$CountName))) +
  scale_fill_manual(values=figPalette,labels=figlabels)+
  #Add proxy sites
  geom_point(data=as.data.frame(proxyDf), aes(x=lonsPrj , y=latsPrj), shape=1,size=0.8) +
  #Format Legend
  theme(plot.background = element_rect(fill = 'white',color='white'),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "in"),
        legend.position = c(0.5,-0.01),
        legend.direction = "horizontal",
        legend.title=element_blank(),
        legend.background=element_rect(colour='black',size=0.4),
        legend.margin=margin(t = 1, r = 1, b = 3, l = -4.5, unit = "pt"),
        legend.key.width  = (unit(35, 'pt')),
        legend.key.height = (unit(5, 'pt')),
        legend.text = element_text(family='Times New Roman',size=8))

if (save) {
  ggsave(plot=proxyMapRegions, width = 6.5, height = 3.25, dpi = 600,
         filename = file.path(wd,"Figures","Proxy",paste('PlotCountByRegion_',var,'.png',sep='')))
}
proxyMapRegions
```
